Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-03 ms.tex
added some notes about the 2013 lower SNR.

\subsection{Subaru HDS Spectra}

@@

>>>>

\subsection{Subaru HDS Spectra}\label{sec:SubaruDescrip}

@@

We posit that the initial analysis of the 2013 Subaru spectrum \citep{kawahara2013starspots} that found a temperature and log(g) of 4950 K and 3.9 log(cm/s$^{-2}$) was affected by insufficient signal to noise in the spectrum.
The 2013 data has a 30\% smaller count rate (in e$^-$/s) than the 2015 data likely because the 2013 weather and guiding were sub-optimal.
On top of that, the total exposure time for the 2013 observations was only 1.5 hours.
The consequence of the increased noise in the 2013 spectra affected the interpretation of this high resolution spectrum.
For example, the SNR of the Na D lines was $\sim$ 30, which is near the threshold needed for the \citet{takeda2005specFGKdwarfs} equivalent width method employed in the initial analysis.
We therefore conclude that the noise in the spectrum affected the stellar parameters rather than gas absorption from sublimating dust grains.
